---
title: "Alarm Systems Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll

---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(tidyverse)
library(ggridges)
```


```{r}
data <- read.csv("/Volumes/bas-analysis/deliverable/all_years.csv")

data.long<- tidyr::gather(data, key='Month', value='AlarmFreq',JUL:JUN, na.rm=TRUE)
```


```{r}
data2 <- read.csv("/Volumes/bas-analysis/deliverable/all_data.csv")
```

```{r}
data3 <- read.csv("/Volumes/bas-analysis/deliverable/all_data_with_dates.csv")
```

```{r}
#divide into years
data21<- data3[(data3$Year==2021),]
data21A <- data21[(data21$Action.a..Failure.f.=="Action"),]
data21F <- data21[(data21$Action.a..Failure.f.!="Action"),]

data22<- data3[(data3$Year==2022),]
data22A <- data22[(data22$Action.a..Failure.f.=="Action"),]
data22F <- data22[(data22$Action.a..Failure.f.!="Action"),]

data23<- data3[(data3$Year==2023),]
data23A <- data23[(data23$Action.a..Failure.f.=="Action"),]
data23F <- data23[(data23$Action.a..Failure.f.!="Action"),]

#Group by month
#months <- data3 %>%
         #group_by(Month) %>%
         #summarise(count = n())
```


2021 
========================================

Row
----------------------------------------

### Total Alarms Requiring Action

```{r}

valueBox(nrow(data21A),
         icon = 'fa-building')
```


### Total Alarms Indicating Status Failure

```{r}

valueBox(nrow(data21F),
         icon = 'fa-building')
```

Column
-------------------------------

### Alarms Requiring Action By Month
```{r}

xform <- list(categoryorder = "array",
              categoryarray = data21A$Month)
p1 <- data21A %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Requiring Action", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

### Alarms Failures By Month
```{r}
xform <- list(categoryorder = "array",
              categoryarray = data21A$Month)
p1 <- data21F %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Indicating Status Failure By Month", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

Column
-------------------------------

### Alarms Requiring Action By Building

```{r}
ph1 <- data21A %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Requiring Action By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph1
```

Column
-------------------------------

### Alarms Indicating Status Failure By Building

```{r}
ph2 <- data21F %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Indicating Status Failure By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph2
```


2022 
========================================

Row
----------------------------------------

### Total Alarms Requiring Action

```{r}
data2022<- data[(data$Year==2022),]
dataA2022<-data2022[(data$Action.Fail=="Action"),]
valueBox(nrow(data22A),
         icon = 'fa-building')
```


### Total Alarms Indicating Status Failure

```{r}
dataF2022<-data2022[(data$Action.Fail=="Fail"),]
valueBox(nrow(data22F),
         icon = 'fa-building')
```

Column
-------------------------------

### Alarms Requiring Action By Month
```{r}

xform <- list(categoryorder = "array",
              categoryarray = data22A$Month)
p1 <- data22A %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Requiring Action", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

### Alarms Failures By Month
```{r}
xform <- list(categoryorder = "array",
              categoryarray = data22A$Month)
p1 <- data22F %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Indicating Status Failure By Month", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

Column
-------------------------------

### Alarms Requiring Action By Building

```{r}
ph1 <- data22A %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Requiring Action By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph1
```

Column
-------------------------------

### Alarms Indicating Status Failure By Building

```{r}
ph2 <- data22F %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Indicating Status Failure By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph2
```


2023 
========================================

Row
----------------------------------------

### Total Alarms Requiring Action

```{r}
data2023<- data[(data$Year==2023),]
dataA2023<-data2023[(data$Action.Fail=="Action"),]
valueBox(sum(dataA2023$Total, na.rm=T),
         icon = 'fa-building')
```


### Total Alarms Indicating Status Failure

```{r}
dataF2023<-data2023[(data$Action.Fail=="Fail"),]
valueBox(sum(dataF2023$Total, na.rm=T),
         icon = 'fa-building')
```

Column
-------------------------------

### Alarms Requiring Action By Month
```{r}

xform <- list(categoryorder = "array",
              categoryarray = data22A$Month)
p1 <- data23A %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Requiring Action", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

### Alarms Failures By Month
```{r}
xform <- list(categoryorder = "array",
              categoryarray = data22A$Month)
p1 <- data23F %>%
         group_by(Month) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Month,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
  layout(title = "Alarms Indicating Status Failure By Month", xaxis = xform,
yaxis = list(title = 'Alarm Frequency'))
p1

```

Column
-------------------------------

### Alarms Requiring Action By Building

```{r}
ph1 <- data23A %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Requiring Action By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph1
```

Column
-------------------------------

### Alarms Indicating Status Failure By Building

```{r}
ph2 <- data23F %>%
         group_by(Building) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Building,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Alarms Indicating Status Failure By Building"),
yaxis = list(title = 'Alarm Frequency'))
ph2
```


Data Table For All Years 
========================================
```{r}
datatest<- select(data.long,-Total)
```

```{r}
datatable(datatest,
          caption = "All Data",
          rownames = T,
          filter = "top",
          options = list(pageLength = 50))
```
